Reading Notes

### 2020-06-23 paper.tex
good section about chemistries of A/D in OPV

Bridging the gap between coarse and atomistic. Specific to polymers. This paper focuses on the mapping of atomistic to CG. (cool! first paper to focus there.) also discussed backmapping. Just noticed this paper is 150 PAGES LONG! OK time to skim.
Polymers have properties which can be measured at many different length scales. diffusions constant can be measured by monitoring the center of gravity of the chains.
It is too big and too slow and also just a bad idea to simulate huge boxes of atomistic polymers. Even if the simulation was to complete, there would be too much information to process accurately. CGing allows scientists to FOCUS their experiments.
start next time section 2 (p8 of 116)
Frozen nuclei approximation is incorrectly referred to as the Born-Oppenheimer approximation?
Quantum chemistry is good for predicting bond and angle potentials but not for LJ because you would need huge basis sets and high order electron correlation. DFT has similar issues LDA results in overbinding and GCA no attraction. partial charges are conformation dependent. 
Quantum chem is very useful for parameterizing dihedrals!
I skimmed this section v heavily but my takeaway is that if you need to know about a chemical reaction (transfer of electrons) it makes sense to consider QC methods. Also QC methods are not the cure-all for making forcefields.
section 3 - how do we get dense systems?
it is hard to change the system once it gets to a dense atomistic representation. so one should start with a good systm! (like from coarse-grain)
This is tough because polymers are dense, amorphous, and highly-connected. three methods exist:
1. add new segments according to the metropolis criterion
2. coarse initials guesses created on a lattice
3. low density condensed step by step using NPT
they described a method of initializing using stream lines and vector fields which results in polymers of constant curvature.
They describe a new rotational move that does a dihedral cis-trans flip.
next time skim through the rest of this paper. I'm over it
\cite{Brini2013}
\cite{Murtola2009a}
\cite{Peter2009d}

>>>>

Bridging the gap between coarse and atomistic. Specific to polymers. This paper focuses on the mapping of atomistic to CG. (cool! first paper to focus there.) also discussed backmapping. Just noticed this paper is 150 PAGES LONG! OK time to skim.
Polymers have properties which can be measured at many different length scales. diffusions constant can be measured by monitoring the center of gravity of the chains.
It is too big and too slow and also just a bad idea to simulate huge boxes of atomistic polymers. Even if the simulation was to complete, there would be too much information to process accurately. CGing allows scientists to FOCUS their experiments.
start next time section 2 (p8 of 116)
Frozen nuclei approximation is incorrectly referred to as the Born-Oppenheimer approximation?
Quantum chemistry is good for predicting bond and angle potentials but not for LJ because you would need huge basis sets and high order electron correlation. DFT has similar issues LDA results in overbinding and GCA no attraction. partial charges are conformation dependent. 
Quantum chem is very useful for parameterizing dihedrals!
I skimmed this section v heavily but my takeaway is that if you need to know about a chemical reaction (transfer of electrons) it makes sense to consider QC methods. Also QC methods are not the cure-all for making forcefields.
section 3 - how do we get dense systems?
it is hard to change the system once it gets to a dense atomistic representation. so one should start with a good systm! (like from coarse-grain)
This is tough because polymers are dense, amorphous, and highly-connected. three methods exist:
1. add new segments according to the metropolis criterion
2. coarse initials guesses created on a lattice
3. low density condensed step by step using NPT
they described a method of initializing using stream lines and vector fields which results in polymers of constant curvature.
They describe a new rotational move that does a dihedral cis-trans flip.
next time skim through the rest of this paper. I'm over it
read mazzio paper!
gave up on baschnagel paper--switching to mazzio!

\cite{Mazzio2015}

oh this paper is so much better. 
opvs are lightwieght, low cost, flexible. Metrics for evaluating these are PCE, Levelized cost of energy (LCOE) and energy payback time (EPBT).
LCOE is life cycle cost/energy produced. EPBT is how long it takes for a device to pay for itself.
start next time at section 2
inorganic: absorptions of photons with energies greater than the band gap results in free charge carriers that can separate at an p-n junction. they can diffuse under external electric field to electrodes.
organic: lower dielectric constant which prevents screening of the attraction between electrons and holes this results in exciton formation rather than free charges. separation of the exciton requires an acceptor/donor interface. if the exciton doesn't reach an interface it will decay back to ground state resulting in the loss of that energy. donor: large ionization potential acceptor: high electron affinity.
different loss mechanisms are discussed: geminate recombination is where the separated charges recombine across the interface. charge recombination where free charges recombine with unassociates charge carriers in a device.
There is some about electrochem which I am reading but not understanding :( external quantum efficiency is a measure of how much current will be produced by a particular wavelength of light. it depends on the efficiency of photoabsorption, exciton diffusion, charge transfer, charge collection.
CHARGE TRANSFER is not the same as CHARGE TRANSPORT
ASTM reference spectra are used now to characterize and standardize OPV
3. Device architectures
some history about opvs: Tang 1979 introduced the two-component donor acceptor active layer with thermally evaporated small molecules. bilayer structure. limited by exciton diffusion length. 
BHJ with fullerene acceptor reported by Yu in 1995 -still state of the art morphology.
diagrams of different device architectures.
start next time on section 4
materials design (aka the good part :D )
good opv acceptor/donors are solution processable, have appropriate band gaps and energy levels, and long planar pi-stacking for good charge carrier mobilities.
regioregularity (head-tail vs head-head p3ht). Mn is the number average molecular weight of the polymers. weight of all polymers/number of chains. Mw is the molecular weight per unit weight of polymer (accounts for size distribution). dispersity is Mw/Mn.
commonly used materials: initially poly(p-phenylene vinylene) (PPV) was very poplar. It was mixed with PCBM (c60) in first reported BHJ solar cells. now we have shifted away towards poly alkyl thiophenes like p3ht.
p3ht/pcbm was max EQE of 76\%. post processing like thermal annealing with externall electric field produced devices with max PCE of 3.5\%. it has been shown the p3ht and pcbm have strong dependence on regioregularity. longer chains are shown to perform better, due to increased mobility with polymer aggregation.
ways to decrease the band gap have become popular using DA polymers (alternating electron rich and electron poor heterocycles) PCDTBT achieved efficiency of 7.5\%. PTB7 had PCE of 7\% and then over 9\% due to promotion of the quinoidal resonance structure using thienothiophene. quinoidal stabilization improves shortcircuit current (Jsc) and fill factor (FF) which increase EQE and IQE so it has good exciton dissociation, charge transport and extraction.
Some small molecule (not polymer) devices show promise.
fullerenes are commonly used as acceptors. the added groups are to help solubility. pc61bm has limited absorption and deep lumo so it can be improved by using pc71bm which is less symmetric and has more allowed optical transitions. indeneC60 is being used to adjust the LUMO level.
next time section5

\cite{Brini2013}
\cite{Murtola2009a}
\cite{Peter2009d}
